Methods Power Study

### 2022-08-15 simulation_study/simulate_summary.Rmd
fix stupid mistake

```{r}
set.seed(895893)
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
```

@@

- We will simulate multiple times at each simulation point:
  - Populations X 100
  - Samples X 100
  - Simulate Researcher X 100

@@

  # after the researcher summary, summarize and stick in dataframe 
  # so we have a dataframe of each population by sample 
  full_simulation[[paste(p, Sys.time(), sep = "_")]] <-
   bind_rows(researcher_summary) %>%
   group_by(scale, original_n, source, name, power) %>%
   summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")

@@

```{r}
# clean up the stuff from the summary 
  summary_long$source <- factor(summary_long$source, 
                                levels = c("low", "med", "high"),
                                labels = c("Low Variance", "Medium Variance", "High Variance"))

  summary_long$scale2 <- factor(summary_long$scale, 
                                levels = c(1:3),
                                labels = c("Small Scale", "Medium Scale", "Large Scale"))

  sd_items <- bind_rows(sd_items1, sd_items2, sd_items3)
  sd_items$original_n <- rep(rep(sizes, each = 3), 3)
  sd_items$source <- rep(c("Low Variance", "Medium Variance", "High Variance"), each = 3*length(sizes))
  summary_long <- summary_long %>% 
    full_join(sd_items, 
              by = c("original_n" = "original_n", "scale" = "scale", 
                     "source" = "source"))

  summary_long$name <- gsub("Percent_Below", "Decile ", summary_long$name)
```

>>>>

```{r}
set.seed(895893) # 233232
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
```

@@

- We will simulate multiple times at each simulation point:
  - Samples X 100
  - Simulate Researcher X 100

@@

  # after the researcher summary, summarize and stick in dataframe 
  # so we have a dataframe of each population by sample 
  full_simulation[[p]] <-
   bind_rows(researcher_summary) %>%
   group_by(scale, original_n, source, name, power) %>%
   summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")

  # clean up the values from the summary while you have the data 
  full_simulation[[p]]$source <- factor(full_simulation[[p]]$source, 
                                levels = c("low", "med", "high"),
                                labels = c("Low Variance", 
                                           "Medium Variance", 
                                           "High Variance"))

  full_simulation[[p]]$scale2 <- factor(full_simulation[[p]]$scale, 
                                levels = c(1:3),
                                labels = c("Small Scale", 
                                           "Medium Scale", 
                                           "Large Scale"))

  # grab the sd information from the pilot sample
  # note this is not the researcher simulated sample 
  sd_items <- bind_rows(deciles$sd_items1, deciles$sd_items2, deciles$sd_items3)
  sd_items$source <- rep(c("Low Variance", 
                           "Medium Variance", 
                           "High Variance"), 
                         each = 3*length(samples$sizes))
  sd_items$original_n <- rep(rep(samples$sizes, each = 3), 3)

  # add together that information 
  full_simulation[[p]] <- full_simulation[[p]] %>% 
    full_join(sd_items, 
              by = c("original_n" = "original_n", 
                     "scale" = "scale", 
                     "source" = "source"))

  full_simulation[[p]]$name <- gsub("Percent_Below", "Decile ", full_simulation[[p]]$name)

@@

## Put Together Data

```{r}
sim_mac <- readRDS("simulation_2022-08-14 12:54:44.Rdata")
sim_win
sim_linux

all_sim <- bind_rows(sim_mac, .id = "id")

summary_long <- all_sim %>% 
  group_by(scale, original_n, source, name, power) %>% 
  summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")
```

## Export Final Data

```{r}

```
